### 2017-10-05 Sections/quantum_channels.tex
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Global spellcheck

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{CNOT_process}
\caption{Process matrix for the CNOT gate, expressed in the Pauli basis. Colour coding: grey=0, white=$1/4$, black=$-1/4$.} \label{fig:CNOT_proc_matrix}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{example_graph}
\caption{The network from Fig.~\ref{fig:example_routes}, with the quantum processes associated with each link. The net process associated with a route is given by the composition of each of the processes over the length of the route. For example, the route \mbox{$R_1=A\to C\to B$} induces the process \mbox{$\mathcal{E}_{R_1} = \mathcal{E}_{C\to B} \circ \mathcal{E}_{A\to C}$}.} \label{fig:example_proc_graph}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{remove_nodes}
\caption{Removing node processes from network graphs on a trivial network with two nodes, $A$ and $B$. Each node is associated with a quantum process ($\mathcal{E}_A$ and $\mathcal{E}_B$). Similarly, each link is associated with a process ($\mathcal{E}_{A\to B}$ and $\mathcal{E}_{B\to A}$). (a) Representation where the node and link processes are shown explicitly. (b) The node processes are replaced with identity operations by replacing each link process with the composition of the link process and its target node process. Equivalently, the cost of each node process is added to the cost of \textit{every} incoming link and then eliminated. The same may be applied for attributes rather than costs. This procedure requires that all links be directed. If undirected links are present, they may simply be replaced by two directed links, one in each direction, implementing identical quantum processes each way.} \label{fig:remove_nodes}
\end{figure}

@@

In the case of optical systems, entirely alternate, but equivalent, approaches may be used, such a probing the Wigner function directly using homodyne detection \cite{???}.

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{CNOT_process}
\caption{Process matrix for the CNOT gate, expressed in the Pauli basis. Colour coding: grey=0, white=$1/4$, black=$-1/4$.} \label{fig:CNOT_proc_matrix}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{example_graph}
\caption{The network from Fig.~\ref{fig:example_routes}, with the quantum processes associated with each link. The net process associated with a route is given by the composition of each of the processes over the length of the route. For example, the route \mbox{$R_1=A\to C\to B$} induces the process \mbox{$\mathcal{E}_{R_1} = \mathcal{E}_{C\to B} \circ \mathcal{E}_{A\to C}$}.} \label{fig:example_proc_graph}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{remove_nodes}
\caption{Removing node processes from network graphs on a trivial network with two nodes, $A$ and $B$. Each node is associated with a quantum process ($\mathcal{E}_A$ and $\mathcal{E}_B$). Similarly, each link is associated with a process ($\mathcal{E}_{A\to B}$ and $\mathcal{E}_{B\to A}$). (a) Representation where the node and link processes are shown explicitly. (b) The node processes are replaced with identity operations by replacing each link process with the composition of the link process and its target node process. Equivalently, the cost of each node process is added to the cost of \textit{every} incoming link and then eliminated. The same may be applied for attributes rather than costs. This procedure requires that all links be directed. If undirected links are present, they may simply be replaced by two directed links, one in each direction, implementing identical quantum processes each way.} \label{fig:remove_nodes}
\end{figure}

@@

In the case of optical systems, entirely alternate, but equivalent, approaches may be used, such a probing the Wigner function directly using homodyne detection \cite{???}\index{Homodyne detection}.

### 2017-10-05 Sections/quantum_genetic_medicine.tex
Global spellcheck

\comment{Add equations for what oracles do}

@@

Doing so will require highly complex processing of massive amounts of genetic and drug information, requiring demanding computational resources. We forsee quantum computing as playing a central role in the processing pipeline of genetic drug development, some initial ideas for which we present here.

@@

Since then, genetic sequencing\index{Genetic sequencing} tools have undergone a massive technological transformation and are now available as commodity hardware at price-points accessible to any well-resourced bioscience lab. This now enables sequencing the human genome orders of magnitude cheaper than the first attempt. It is now possible to map the genome for $\sim$\$1,000's.

Following its own technological Moore's Law\index{Moore's Law}, one can reasonably anticipate this process becoming sufficiently cheap that in the near future it will become economically viable for every individual to have their own personal genome fully sequenced and available for medical use.

@@

Open-source software for implementing \textit{de novo} assembly of short-read data is available. The well-known \textit{Velvet}\index{Velvet} package \cite{velvet}\index{Velvet} does this graph theoretically using de Bruijn graph\index{de Bruijn graphs} representations for contigs/reads, with very efficient computational resource requirements.

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Reference genome}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexiblity offered by this threshold acommodates for mutational differences between the reference and the short-reads\index{Genetic mutations}, which is ultimately what we wish to characterise.

To illustrate the power of this approach, consider the following. Only a miniscule fraction of the genome differs from one individual to the next -- almost all of it is identical. Thus, mapping allows us to identify the mutational differences between individuals. Importantly, unlike \textit{de novo} sequencing, short-reads can be mapped to the reference even with incomplete data -- contig `islands'\index{Contig islands} needn't remain so. Non-overlapping short-reads can still be successfully mapped, making this approach applicable (but potentially incomplete) even with datasets insufficiently large for \textit{de novo} sequencing to be effective.

@@

As with \textit{de novo} sequencing, efficient open-source software for efficiently implementing mapping using commodity hardware is available \cite{Bfast etc}.

@@

The drug design process for conventional medicines is an incredibly tedious one, requiring massive latitudinal and longitudinal studies of the effects of drugs on physiological symptoms. However, in the case of individually tailored medicine such studies are clearly not possible. This will require replacing human studies with accurate biomolecular-level simulations of these chemical processes. At this scale, interactions are inevitably quantum mechanical in nature, which must be accomodated for in simulations.

@@

These approaches borrowed from quantum chemistry allow simulation of the interaction between drug compounds and molecular biochemical interactions. The next step is to perform this process against a huge library of candidate drug compounds\index{Drug compound libraries}, ligands\index{Ligand libraries} or functional groups\index{Functional group libraries}, from which, we hope, some candidates will exhibit desired characteristics, such as bonding affinities\index{Bonding affinity}.

To achieve this, let use construct a classical algorithm for exhaustively constructing and enumerating organic drug molecules or functional groups, up to some cutoff size\index{Cutoff size}. The length of this list grows exponentially with the cutoff size. Next we implement this algorithm unitarily (which is always possible, writing the classical circuit as a reversible one), and construct it as a quantum oracle\index{Oracle} such that every input state (which acts as a pointer\index{Pointers} to an element in the list) yields as output a qubit representation\index{Qubit molecule representation} of the corresponding drug compound. Specifically, the oracle implements a transformation of the form,
\begin{align}
\hat{U}_\mathrm{oracle}\ket{i}\ket{0}^{\otimes n} \to \ket{i}\ket{\psi_i}_\mathrm{molecule}^{(n)},
\end{align}
where $i$ is the index (pointer) to the drug element in the enumeration, and $n$ is the number of qubits encoding the representation of the drug molecule\footnote{This may be implemented unitarily, which is easy to see via its preservation of orthonormality.}.

Having contructed this oracle, we feed the output qubit molecule description into the Hamiltonian simulation algorithm\index{Quantum simulation}, with exponential speedup, yielding as output a `score' characterising some desired property of the interaction, such as bonding affinity\index{Bonding affinity}. The joint oracle-simulation algorithm is finally embedded within a quantum search subroutine\index{Quantum search algorithm}, which searches over the input space enumerating the set of drug candidates for scores above some desired threshold. This yields a quadratic enhancement in the number of drug candidates that can be simulated in parallel.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.25\textwidth]{genetic_medicine_pipeline}
	\caption{Pipeline for quantum-enhanced genetic drug development. A quantum search algorithm searches over algorithmically-generated drug compounds, for each performing Hamiltonian simulation, to determine if the compound's score is above a threshold. The quantum search subroutine yields a quadratic enhancement in the number of drugs that can be simulated in parallel, and the Hamiltonian simulation subroutine yields an exponential enhancement over classical simulation techniques.} \label{fig:genetic_med_pipe}
\end{figure}

>>>>

\comment{Add equations to what Hamiltonian simulation subroutine does, or reference back to algorithms section.}

@@

Doing so will require highly complex processing of massive amounts of genetic and drug information, requiring demanding computational resources. We foresee quantum computing as playing a central role in the processing pipeline of genetic drug development, some initial ideas for which we present here.

@@

Since then, genetic sequencing\index{Genetic sequencing} tools have undergone a massive technological transformation and are now available as commodity hardware at price-points accessible to any well-resourced bioscience lab. This now enables sequencing the human genome orders of magnitude cheaper than the first attempt. It is now possible to map a genome for $\sim$\$1,000's.

Following its own technological Moore's Law\index{Moore's Law}, one can reasonably anticipate this process becoming sufficiently cheap that in the near future it will become economically viable for every individual to have their own personal genome fully sequenced and available for medical use.f

--- \textit{Benedictus benedicat}.

@@

Open-source software for implementing \textit{de novo} assembly of short-read data is available. The well-known \textit{Velvet}\index{Velvet} package \cite{velvet}\index{Velvet} does this graph-theoretically using de Bruijn graph\index{de Bruijn graphs} \cite{???} representations for contigs/reads, with very efficient computational resource requirements.

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Reference genome}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexibility offered by this threshold accommodates for mutational differences between the reference and the short-reads\index{Genetic mutations}, which is ultimately what we wish to characterise.

To illustrate the power of this approach, consider the following. Only a minuscule fraction of the genome differs from one individual to the next -- almost all of it is identical. Thus, mapping allows us to identify the mutational differences between individuals. Importantly, unlike \textit{de novo} sequencing, short-reads can be mapped to the reference even with incomplete data -- contig `islands'\index{Contig islands} needn't remain so. Non-overlapping short-reads can still be successfully mapped, making this approach applicable (but potentially incomplete) even with datasets insufficiently large for \textit{de novo} sequencing to be effective.

@@

As with \textit{de novo} sequencing, open-source software for efficiently implementing mapping using commodity hardware is available \cite{Bfast etc}.

@@

The drug design process for conventional medicines is an incredibly tedious one, requiring massive latitudinal and longitudinal studies on the effects of drugs on physiological symptoms. It is not uncommon for the entire drug development process, from design, to testing, to approval, to cost on the order of $\sim$\$100m's for a single drug. However, in the case of individually tailored medicine such studies are clearly not possible. This will require replacing human studies with accurate biomolecular-level simulations of these chemical processes. At this scale, interactions are inevitably quantum mechanical in nature, which must be accommodated for in simulations.

@@

These approaches borrowed from quantum chemistry allow simulation of the interaction between drug compounds and molecular biochemical interactions. The next step is to perform this process against a huge library of candidate drug compounds\index{Drug compound libraries}, ligands\index{Ligand libraries} or functional groups\index{Functional group libraries}, from which, we hope, some candidates will exhibit desired characteristics, such as strong bonding affinities\index{Bonding affinity}.

To achieve this, let us construct a classical algorithm for exhaustively constructing and enumerating organic drug molecules or functional groups, up to some cutoff size\index{Cutoff size}. The length of this list grows exponentially with the cutoff size. Next we implement this algorithm unitarily (which is always possible, writing the classical circuit as a reversible one), and construct it as a quantum oracle\index{Oracle} such that every input state (which acts as a pointer\index{Pointers} to an element in the list) yields as output a qubit representation\index{Qubit molecule representation} of the corresponding drug compound. Specifically, the oracle implements a transformation of the form,
\begin{align}
\hat{U}_\mathrm{oracle}\ket{i}\ket{0}^{\otimes n} \to \ket{i}\ket{\psi_i}_\mathrm{molecule}^{(n)},
\end{align}
where $i$ is the index (pointer) to the drug element in the enumeration, and $n$ is the number of qubits encoding the representation of the drug molecule\footnote{This may be implemented unitarily, which is easy to see via its preservation of orthonormality.}.

Having constructed this oracle, we feed the output qubit molecule description into the Hamiltonian simulation algorithm\index{Quantum simulation}, with exponential speedup, yielding as output a `score' characterising some desired property of the interaction, such as bonding affinity\index{Bonding affinity}. The joint oracle$\to$simulation algorithm is finally embedded within a quantum search subroutine\index{Quantum search algorithm}, which searches over the input space enumerating the set of drug candidates for scores above some desired threshold. This yields a quadratic enhancement in the number of drug candidates that can be simulated in parallel. Successful search results, where a compound achieves the threshold score, are then tagged for further investigation as treatment drug candidates.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.25\textwidth]{genetic_medicine_pipeline}
	\caption{Pipeline for quantum-enhanced genetic drug development. A quantum search algorithm searches over algorithmically-generated drug compounds or functional groups, for each performing Hamiltonian simulation, to determine if its score is above a threshold. The quantum search subroutine yields a quadratic enhancement in the number of drugs that can be simulated in parallel, and the Hamiltonian simulation subroutine yields an exponential enhancement over classical simulation techniques.} \label{fig:genetic_med_pipe}
\end{figure}

### 2017-10-05 Sections/the_quantum_space_race.tex
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Global spellcheck

One of the major hurdles that must be overcome before quantum networks achieve widespread commercial use is to span large distances between nodes distributing entanglement as a resource. The key technological and commercial centers of the world are decentralised, spread across the globe, hence connections over intercontinental distances are necessary, with nodes separated potentially by thousands of kilometers. This distance is one of the major challenges facing the creation of large-scale quantum networks.

The most convenient way of transmitting quantum information is using optical fibers\index{Optical fibers}. However, it is well-known that due to the exponential scaling of loss with distance, the upper limit is of the order of several hundred kilometers. This shortcoming has inspired intensive research into extending these distances using quantum repeaters, discussed in detail in Sec.~\ref{sec:rep_net}\index{Repeater networks}.

An alternative to fiber optic communication is using terrestrial free-space links\index{Terrestrial free-space communication}. Particular wavelength regimes exhibit low absorption\index{Absorption}, allowing the propagation of photons across large distances. Impressive experimental demonstrations of teleportation with free-space entanglement by Zeilinger \textit{et al.} \cite{bib:ursin07, bib:ma2012quantum, bib:yin2013lower} over 100km have been achieved.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{distance_to_horizon}
\caption{Distance to the horizon $d$ (in kilometers), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughtly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realisitic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}

@@

As we describe more in the next section, several recent positive results have made the technology an immediate possibility in realizing such a global level quantum network. In this section, we summarize the current technological state of the art internationally, and discuss some of the remaining major challenges.

@@

\begin{figure*}[!htb]
\includegraphics[width=\linewidth]{space_1}
\caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=\linewidth]{space_4}
\caption{The Chinese Micius quantum communications satellite. (a) Schematic of the satellite and ground stations used to observe the entangled photons \cite{bib:popkin17}. \comment{[TB: Took image from Science News, may need permission]. Picture is watermarked}. (b) Attenuation during entanglement distribution from \cite{bib:yin2017satellite}. (c) Fidelities achieved for teleportation of various states as marked from \cite{bib:ren2017ground}.}
\label{fig:space_4}
\end{figure*}

@@

In 2016, the group at the University of Science \& Technology China (USTC), led by Jian-Wei Pan\index{Jian-Wei Pan}, launched QUESS (Quantum Science Experiment Satellite), a quantum communication satellite \cite{bib:gibney16, bib:xin11}. The main feature of the satellite is an ultrabright source of polarization entangled photons at a wavelength of 810nm, generated by SPDC\index{Spontaneous parametric down-conversion (SPDC)}. The source is capable of emitting $5.9 \times 10^6$ photon-pairs per second with a fidelity of $\sim 0.91$.

@@

The attenuation of the photons during the downlink transmission is shown in Fig.~\ref{fig:space_4}(b). Taking into account the photon transmission distances, the attenuation rates are far better than the best performance of optical fibers at 0.16dB/km \cite{bib:yin2013lower} and even theoretical loss limits. The Bell violation recorded in this experiment was at the level of $2.37\pm 0.09>2$ \comment{Does this need units or a variable name?}, and the non-locality\index{Non-locality} of the entanglement was confirmed.

The second experiment performed ground-to-satellite\index{Ground-to-satellite communication} QST\index{Quantum state teleportation} \cite{bib:ren2017ground}. Here a single polarization-encoded photon defines the qubit to be teleported, and the satellite acts as the receiver. The entangled photons are generated on the ground, at the observatory in Ngari, Tibet. As with the first experiment described above, the satellite is in LEO and sweeps across the sky, creating a narrow time-window during which the teleportation must be achieved. The longest distance for successful teleportation was $\sim 1400$km, when the satellite emerges from the horizon. When directly overhead, the satellite is at a distance of $\sim 500$km. As Fig.~\ref{fig:space_4}(c) shows, the fidelity of the types of states teleported are all above the theoretical classical bound of $2/3$, with an average of $0.80 \pm 0.01$.

@@

\subsubsection{Japan: SOCRATES}\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)}) is a microsatellite\index{Microsatellite} developed by NICT (National Institute of Information \& Communications Technology\index{National Institute of Information \& Communications Technology (NICT)}) \cite{bib:horiuchi2015view, bib:toyoshima2015current, bib:takenaka2017}. This is a 48kg satellite of volume $50^3$cm$^3$ that demonstrates multi-purpose (i.e. both classical and quantum) optical communication. Its primary mission is to demonstrate laser communication in space. As one of its subgoals, the on-board equipment is adapted to perform QKD experiments\index{Quantum key distribution (QKD)}. To this end, the satellite is equipped with a photon source, where the polarization can be classially switched between non-orthogonal angles, necessary for BB84\index{BB84 protocol} for example.

Initial results indicated polarization preservation of photons emitted from the satellite, a preliminary step towards performing protocols such as BB84\index{BB84 protocol} \cite{bib:carrasco2016leo}. More recent results showed quantum limited satellite-to-ground\index{Satellite-to-ground} communication was possible, attaining a quantum bit error rate below 5\% \cite{bib:takenaka2017} during the closest approach of the satellite to the ground at a distance of 744km. The downlink was established over distances of over 1,000km, although for obvious reasons the error rate was higher for longer distances.

@@

The group at the National University of Singapore (NUS)\index{National University of Singapore (NUS)} also has taken the approach of using nanosatellites\index{Nanosatellite}, with the capability of generating correlated photon-pairs on-board \cite{bib:tang2016generation}. The nanosatellite weighs just 1.65kg and has all the components required for creating and detecting SPDC photon pairs. The nanosatellite approach greatly reduces the cost of space-launch, and the launch itself was performed by the Indian space agency \comment{What's it called}. As photon generation and detection are both on the same satellite, no quantum communications channel (to other satellites or Earth) was established in the experiment, although it demonstrated in-principle the space-worthiness of the basic hardware components.

@@

The QEYSSat (Quantum EncrYption \& Science Satellite) proposes a microsatellite that incorporates a quantum receiver \cite{bib:jennewein2014qeyssat}. The satellite acts as a trusted node\index{Trusted nodes}, to which photons would be transmitted from Earth-based sources. This could be employed to perform QKD between two locations on Earth that are separated by large distances. No photon sources or quantum memories would be included on the QEYSSat.

\begin{figure*}[!htb]
\includegraphics[width=\linewidth]{space_2}
\caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}.}
\label{fig:space_2}
\end{figure*}

@@

For applications such as quantum clock synchronization\index{Quantum clock synchronisation} (Sec.~\ref{sec:clock_sync}) and experiments testing fundamental physics at large length-scales and velocities (Sec.~\ref{sec:fundamental_physics}), it is likely that extremely high fidelities of quantum operations will be required. For example, for clock synchronization, even current atomic clocks\index{Atomic clocks} used as national standards have an accuracy at the level of $10^{-14}$\comment{Units for this?}. Thus, such high-precision experiments will almost certainly follow the less demanding QKD experiments.

As the precision of technology improves, other sources of error may appear which may require correction. It is well-known from existing GPS satellites\index{Global positioning system (GPS)}, that it is crucial to account for relativistic effects\index{Relativistic effects}, due to time-dilation\index{Time-dilation} and the gravitational red-shift\index{Gravitational red-shift}. Not accounting for these effects would seriously compromise the GPS system, with inaccuracies equating to an error on the order of 10km/day. This is due to the high velocities of LEO\index{Low Earth orbit} satellites, traveling at speeds of $\beta = 10^{-5}$ times the speed of light. Such relativistic effects can affect entanglement in the presence of diffracting photons \cite{bib:gingrich03}\index{Diffraction}. Even for single-photon transmission, polarization-encoded photons can give rise to corrections at the order of $\beta$ \cite{bib:byrnes2017lorentz} \comment{Not sure what this means? What correction?}. Relativistically invariant entanglement distribution protocols\index{Relativistically invariant entanglement distribution} have been proposed to avoid such effects, which would otherwise require correction \cite{bib:yurtsever02, bib:li2003relativistic, bib:byrnes2017lorentz}.

>>>>

One of the major hurdles that must be overcome before quantum networks achieve widespread commercial use is to span large distances between nodes distributing entanglement as a resource. The key technological and commercial centres of the world are decentralised, spread across the globe, hence connections over intercontinental distances are necessary, with nodes separated potentially by thousands of kilometres. This distance is one of the major challenges facing the creation of large-scale quantum networks.

The most convenient way of transmitting quantum information is using optical fibres\index{Optical fibres}. However, it is well-known that due to the exponential scaling of loss with distance, the upper limit is of the order of several hundred kilometres. This shortcoming has inspired intensive research into extending these distances using quantum repeaters, discussed in detail in Sec.~\ref{sec:rep_net}\index{Repeater networks}.

An alternative to fibre optic communication is using terrestrial free-space links\index{Terrestrial free-space communication}. Particular wavelength regimes exhibit low absorption\index{Absorption}, allowing the propagation of photons across large distances. Impressive experimental demonstrations of teleportation with free-space entanglement by Zeilinger \textit{et al.} \cite{bib:ursin07, bib:ma2012quantum, bib:yin2013lower} over 100km have been achieved.

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{distance_to_horizon}
\caption{Distance to the horizon $d$ (in kilometres), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realistic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}

@@

As we describe more in the next section, several recent positive results have made the technology an immediate possibility in realising such a global level quantum network. In this section, we summarise the current technological state of the art internationally, and discuss some of the remaining major challenges.

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_1}
\caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_4}
\caption{The Chinese Micius quantum communications satellite. (a) Schematic of the satellite and ground stations used to observe the entangled photons \cite{bib:popkin17}. \comment{[TB: Took image from Science News, may need permission]. Picture is watermarked}. (b) Attenuation during entanglement distribution from \cite{bib:yin2017satellite}. (c) Fidelities achieved for teleportation of various states as marked from \cite{bib:ren2017ground}.}
\label{fig:space_4}
\end{figure*}

@@

In 2016, the group at the University of Science \& Technology China (USTC), led by Jian-Wei Pan\index{Jian-Wei Pan}, launched QUESS (Quantum Science Experiment Satellite), a quantum communication satellite \cite{bib:gibney16, bib:xin11}. The main feature of the satellite is an ultra-bright source of polarisation entangled photons at a wavelength of 810nm, generated by SPDC\index{Spontaneous parametric down-conversion (SPDC)}. The source is capable of emitting $5.9 \times 10^6$ photon-pairs per second with a fidelity of $\sim 0.91$.

@@

The attenuation of the photons during the downlink transmission is shown in Fig.~\ref{fig:space_4}(b). Taking into account the photon transmission distances, the attenuation rates are far better than the best performance of optical fibres at 0.16dB/km \cite{bib:yin2013lower} and even theoretical loss limits. The Bell violation recorded in this experiment was at the level of $2.37\pm 0.09>2$ \comment{Does this need units or a variable name?}, and the non-locality\index{Non-locality} of the entanglement was confirmed.

The second experiment performed ground-to-satellite\index{Ground-to-satellite communication} QST\index{Quantum state teleportation} \cite{bib:ren2017ground}. Here a single polarisation-encoded photon defines the qubit to be teleported, and the satellite acts as the receiver. The entangled photons are generated on the ground, at the observatory in Ngari, Tibet. As with the first experiment described above, the satellite is in LEO and sweeps across the sky, creating a narrow time-window during which the teleportation must be achieved. The longest distance for successful teleportation was $\sim 1400$km, when the satellite emerges from the horizon. When directly overhead, the satellite is at a distance of $\sim 500$km. As Fig.~\ref{fig:space_4}(c) shows, the fidelity of the types of states teleported are all above the theoretical classical bound of $2/3$, with an average of $0.80 \pm 0.01$.

@@

\subsubsection{Japan: SOCRATES}\index{Space Optical Communications Research Advanced Technology Satellite (SOCRATES)}) is a micro-satellite\index{Micro-satellite} developed by NICT (National Institute of Information \& Communications Technology\index{National Institute of Information \& Communications Technology (NICT)}) \cite{bib:horiuchi2015view, bib:toyoshima2015current, bib:takenaka2017}. This is a 48kg satellite of volume $50^3$cm$^3$ that demonstrates multi-purpose (i.e. both classical and quantum) optical communication. Its primary mission is to demonstrate laser communication in space. As one of its subgoals, the on-board equipment is adapted to perform QKD experiments\index{Quantum key distribution (QKD)}. To this end, the satellite is equipped with a photon source, where the polarisation can be classically switched between non-orthogonal angles, necessary for BB84\index{BB84 protocol} for example.

Initial results indicated polarisation preservation of photons emitted from the satellite, a preliminary step towards performing protocols such as BB84\index{BB84 protocol} \cite{bib:carrasco2016leo}. More recent results showed quantum limited satellite-to-ground\index{Satellite-to-ground} communication was possible, attaining a quantum bit error rate below 5\% \cite{bib:takenaka2017} during the closest approach of the satellite to the ground at a distance of 744km. The downlink was established over distances of over 1,000km, although for obvious reasons the error rate was higher for longer distances.

@@

The group at the National University of Singapore (NUS)\index{National University of Singapore (NUS)} also has taken the approach of using nano-satellites\index{Nano-satellite}, with the capability of generating correlated photon-pairs on-board \cite{bib:tang2016generation}. The nano-satellite weighs just 1.65kg and has all the components required for creating and detecting SPDC photon pairs. The nano-satellite approach greatly reduces the cost of space-launch, and the launch itself was performed by the Indian space agency \comment{What's it called}. As photon generation and detection are both on the same satellite, no quantum communications channel (to other satellites or Earth) was established in the experiment, although it demonstrated in-principle the space-worthiness of the basic hardware components.

@@

The QEYSSat (Quantum EncrYption \& Science Satellite) proposes a micro-satellite\index{Micro-satellite} that incorporates a quantum receiver \cite{bib:jennewein2014qeyssat}. The satellite acts as a trusted node\index{Trusted nodes}, to which photons would be transmitted from Earth-based sources. This could be employed to perform QKD between two locations on Earth that are separated by large distances. No photon sources or quantum memories would be included on the QEYSSat.

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_2}
\caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}.}
\label{fig:space_2}
\end{figure*}

@@

For applications such as quantum clock synchronisation\index{Quantum clock synchronisation} (Sec.~\ref{sec:clock_sync}) and experiments testing fundamental physics at large length-scales and velocities (Sec.~\ref{sec:fundamental_physics}), it is likely that extremely high fidelities of quantum operations will be required. For example, for clock synchronisation, even current atomic clocks\index{Atomic clocks} used as national standards have an accuracy at the level of $10^{-14}$\comment{Units for this?}. Thus, such high-precision experiments will almost certainly follow the less demanding QKD experiments.

As the precision of technology improves, other sources of error may appear which may require correction. It is well-known from existing GPS satellites\index{Global positioning system (GPS)}, that it is crucial to account for relativistic effects\index{Relativistic effects}, due to time-dilation\index{Time-dilation} and the gravitational red-shift\index{Gravitational red-shift}. Not accounting for these effects would seriously compromise the GPS system, with inaccuracies equating to an error on the order of 10km/day. This is due to the high velocities of LEO\index{Low Earth orbit} satellites, traveling at speeds of $\beta = 10^{-5}$ times the speed of light. Such relativistic effects can affect entanglement in the presence of diffracting photons \cite{bib:gingrich03}\index{Diffraction}. Even for single-photon transmission, polarisation-encoded photons can give rise to corrections at the order of $\beta$ \cite{bib:byrnes2017lorentz} \comment{Not sure what this means? What correction?}. Relativistically invariant entanglement distribution protocols\index{Relativistically invariant entanglement distribution} have been proposed to avoid such effects, which would otherwise require correction \cite{bib:yurtsever02, bib:li2003relativistic, bib:byrnes2017lorentz}.
